---
title: "Look Over Korean Immigrants Life Style!"
date: "Nov 16, 2015"
author : "Daehan Park, Seungjin Lee, Byeol Yeo, Jinhyuk Choi, Yoonyoung Choi at Bigdata Club BOAZ in Korea"
output: 
  html_document:
    theme: united
---

##0. Data Preparation
```{r}
suppressMessages({  
  library(data.table)
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  library(RColorBrewer)
  library(maps)
})

path <- "N:\\My_Documents\\2013 USA Census\\WD\\Data"
cols <- c("COW", "POBP", "ANC1P", "RAC2P", "DECADE", "ST", "SEX", "YOEP", "AGEP", "INDP", "SCHL", "WKHP", "PINCP")
pusa <- fread(paste(path, "ss13pusa.csv", sep = "\\"), select = cols)
pusb <- fread(paste(path, "ss13pusb.csv", sep = "\\"), select = cols)
pus <- bind_rows(pusa, pusb)
rm(pusa, pusb)
gc()

# COW(Class of worker)
pus$COW <- factor(pus$COW)
levels(pus$COW) <- c("Private profit", "Private non-profit", "Local government", "State government", "Federal government", "Self-employed", "Self-employed", "Working without pay", "Unemployed")

# DECADE(Decade of entry)
pus$DECADE <- factor(pus$DECADE)
levels(pus$DECADE) <- c("~1950's", "1950's", "1960's", "1970's", "1980's", "1990's", "2000's~")

# ST(State Code)
pus$ST <- as.factor(pus$ST)
levels(pus$ST) <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut",
                 "Delaware", "District of Columbia", "Florida", "Georgia", "Hawaii", "Idaho", "Illinois",
                 "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts",
                 "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", 
                 "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota",
                 "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota",
                 "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia",
                 "Wisconsin", "Wyoming", "Puerto Rico")

# SEX
pus$SEX <- factor(pus$SEX)
levels(pus$SEX) <- c("Male", "Female")

# INDP(Industry recode for 2013 and later based on 2012 IND codes)
pus$INDP <- ifelse(pus$INDP >= 170 & pus$INDP <= 290, 170, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 370 & pus$INDP <= 490, 370, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 570 & pus$INDP <= 770, 570, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 1070 & pus$INDP <= 3990, 1070, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 4070 & pus$INDP <= 6390, 4070, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 6470 & pus$INDP <= 6780, 6470, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 6870 & pus$INDP <= 7190, 6870, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 7270 & pus$INDP <= 7790, 7270, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 7860 & pus$INDP <= 7890, 7860, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 7970 & pus$INDP <= 8290, 7970, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 8370 & pus$INDP <= 8470, 8370, pus$INDP)
pus$INDP <- ifelse(pus$INDP %in% c(8660, 8680, 8690), 8370, pus$INDP) 
pus$INDP <- ifelse(pus$INDP >= 8770 & pus$INDP <= 9290, 8370, pus$INDP)
pus$INDP <- ifelse(pus$INDP %in% c(8560, 8570, 8580, 8590, 8670), 8560, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 9370 & pus$INDP <= 9590, 9370, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 9670 & pus$INDP <= 9870, 9670, pus$INDP)
pus$INDP <- ifelse(pus$INDP >= 9920, 9920, pus$INDP)
pus$INDP <- factor(pus$INDP)
levels(pus$INDP) <- c("Agriculture, Forestry, Fishing, Hunting", "Mining", "Utilities, Construction", 
              "Manufacturing", "Trade, Logistic", "Information, Communications", "Finance",
              "Professional", "Education", "Health", "Other Services",
              "Arts, Entertainment", "Public Administration", "Military", "Unemployed"
            )

# SCHL(Educational attainment)
pus$SCHL <- ifelse(pus$SCHL <= 16, 16, pus$SCHL)
pus$SCHL <- ifelse(pus$SCHL >= 17 & pus$SCHL <= 19, 19, pus$SCHL)
pus$SCHL <- factor(pus$SCHL)
levels(pus$SCHL) <- c("High school or lower", "Some college", "Associate", "Bachelor", "Master", "Professional", "Doctorate")
```
  
  
##1. Comparing different immigrants group for working hours per week  
  
 We would like to know that there are significant differences for working hours among ethnic immigrants group. According to the OECD statistics, Koreans are working 1.2 times longer on average than other developed countries.(<https://data.oecd.org/emp/hours-worked.htm>)
  
```{r}
# OECD Data
oecd.wh <- read.csv("N:\\My_Documents\\2013 USA Census\\WD\\History\\OECD_Work hour.csv")
oecd.wh <- filter(oecd.wh, LOCATION %in% c("DEU", "ISR", "KOR", "MEX", "SWE"))

ggplot(oecd.wh, aes(x=LOCATION)) + geom_bar(aes(y=Value, fill=LOCATION), stat="identity")
```

 In the USA census data, we can find Korean immigrants are still number 2 among five ethnic immigrants group. 

```{r}
WH <- pus[, c("COW", "POBP", "ANC1P", "WKHP")]
WH$NATION <- rep(NA)
WH$NATION <- ifelse(WH$POBP == 217 & WH$ANC1P ==750, "Korea", WH$NATION)
WH$NATION <- ifelse(WH$POBP == 214 & WH$ANC1P == 419, "Israel", WH$NATION)
WH$NATION <- ifelse(WH$POBP == 110 & WH$ANC1P == 32, "German", WH$NATION)
WH$NATION <- ifelse(WH$POBP == 303 & WH$ANC1P == 210, "Mexico", WH$NATION)
WH$NATION <- ifelse(WH$POBP == 136 & WH$ANC1P == 89, "Sweden", WH$NATION)

```

```{r, fig.width=9, fig.height=7}
ggplot(filter(WH, is.na(NATION)==F) , aes(x=NATION, y=WKHP)) + 
    geom_boxplot(aes(fill=NATION), size=0.3) +
    stat_summary(fun.y=mean, geom="point", shape=23, size=3) + 
    ggtitle("Working hours per week")
```

```{r}
WH %>% 
    group_by(NATION) %>%
        select(WKHP) %>% 
            summarise(Avg.Work.Hour=mean(WKHP, na.rm=T))
```
 

### Self employed group  
  
 Especially, in self-employed groups there are more significant distributional differences. Certainly, __Israel__ and __Korean__ immigrants’ distribution converge in higher working hours than other ethnic groups.  
  
```{r}
WHSE <- filter(WH, COW == "Self-employed")

```

```{r, fig.width=9, fig.height=7}
ggplot(filter(WHSE, is.na(NATION)==F), aes(x= NATION, y= WKHP)) + 
    geom_boxplot(aes(fill = NATION), alph= 0.5) +
    stat_summary(fun.y=mean, geom="point", shape=23, size=4) + 
    ggtitle("Working hours of self-employer per week")
```

```{r}
WHSE %>% 
    group_by(NATION) %>%
        select(WKHP) %>% 
            summarise(Avg.Work.Hour=mean(WKHP, na.rm=T))
```


##2. A study on the periodic characteristics of korean immigrants?!
### Age Distribution by Decade on Their Immigrants Year

 We divide Korean immigrants by decade on their immigrants year. Using this, we look over their age distribution. In natural, More far from their immigrants year, more older.  
   
```{r}
pus.kor <- filter(pus, POBP == 217 & RAC2P == 49) # POBP : 217(Korea), RAC3P : 49(Korean)

```

```{r, fig.width=9, fig.height=6}
# DECADE
ggplot(pus.kor, aes(AGEP, group=DECADE)) + 
  geom_bar(aes(colour=DECADE, fill=DECADE), binwidth=1, alpha=0.9) +
  xlab("Age") + ylab("Count") + ggtitle("Age by Decade")
```

```{r}
table(pus.kor$DECADE)
```


### Living State
 Most korean immigrants live in __California__.
```{r}
all_state <- map_data("state")
data <- as.data.frame(prop.table(table(pus.kor$ST)))
data$state <- sort(tolower(c("district of columbia","Puerto Rico", state.name)))
all_state$freq <- data$Freq[match(all_state$region, data$state)]*100
```

```{r, fig.width=9, fig.height=6}
p <- ggplot(all_state, aes(x=long, y=lat, group=group)) + 
      geom_polygon(aes(fill=freq), colour="gray78") + 
      scale_fill_gradient(name="Proportion", low="white", high="blueviolet")
p <- p + theme(strip.background = element_blank(),
               strip.text.x     = element_blank(),
               axis.text.x      = element_blank(),
               axis.text.y      = element_blank(),
               axis.ticks       = element_blank(),
               axis.line        = element_blank(),
               panel.background = element_blank(),
               panel.border     = element_blank(),
               panel.grid       = element_blank(),
               legend.position  = "right") +
          xlab("") + ylab("") + ggtitle("Avg. Number of Korean by State")
p
```

```{r}
st.df <- pus.kor %>% group_by(ST) %>% summarise(Count=n()) %>% arrange(desc(Count))
st.df$Prop <- round(st.df$Count / sum(st.df$Count) * 100, 1)
head(st.df, 20)
```


###1950~60's  

 This graph shows sex ratio by decade. All of decade, female ratio is more higher than that of male. But 1950’s have most high ratio. There are some historical reasons to explain this phenomenon. In 1950" Korean War, there were lots of wife who are married US Armed Forces in Korea. So when army went back their country(US), Korean female wife followed them. Since 1950, Ratio of female have  increased until recent date.
 
```{r, fig.width=9, fig.height=6}
ggplot(pus.kor, aes(x=DECADE)) + 
    geom_bar(aes(fill=SEX), position="fill") + 
    xlab("COUNT") + ggtitle("Sex Ratio by Decade")
```

 Also, we would like to know immigrants age distribution at the time when they immigrant. This graph shows Korean immigrants age group at the time when they immigrant year. Before observing the data, we divided age group by decade. The graph shows striking pattern before __1950’s__ and __1950’s__. That time, lots of youth came in USA. It seems that it is influenced by the Korea War. However, there are some limitations. The data comes from 2013 USA census, so there are few or no sampling targets from elder people.

```{r}
pus.kor$AGEY <- pus.kor$AGEP - (2013-pus.kor$YOEP) + 2
pus.kor$AGEG <- rep(0, nrow(pus.kor))
pus.kor$AGEG <- ifelse(pus.kor$AGEY >= 0 & pus.kor$AGEY < 10, 0, pus.kor$AGEG)
pus.kor$AGEG <- ifelse(pus.kor$AGEY >= 10 & pus.kor$AGEY < 20, 1, pus.kor$AGEG)
pus.kor$AGEG <- ifelse(pus.kor$AGEY >= 20 & pus.kor$AGEY < 30, 2, pus.kor$AGEG)
pus.kor$AGEG <- ifelse(pus.kor$AGEY >= 30 & pus.kor$AGEY < 40, 3, pus.kor$AGEG)
pus.kor$AGEG <- ifelse(pus.kor$AGEY >= 40 & pus.kor$AGEY < 50, 4, pus.kor$AGEG)
pus.kor$AGEG <- ifelse(pus.kor$AGEY >= 50 & pus.kor$AGEY < 60, 5, pus.kor$AGEG)
pus.kor$AGEG <- ifelse(pus.kor$AGEY >= 60, 6, pus.kor$AGEG)
pus.kor$AGEG <- factor(pus.kor$AGEG)
levels(pus.kor$AGEG) <- c("0's", "10's", "20's", "30's", "40's", "50's", "60's~")
```

```{r, fig.width=9, fig.height=6}
ggplot(pus.kor, aes(x=DECADE)) + 
    geom_bar(aes(fill=AGEG), position="fill") +
    ggtitle("Age Group at Immigrant Year")
```

```{r}
table(pus.kor$DECADE,pus.kor$AGEG)
```

 This graph shows that Korean immigrants’s industry distribution by decade. In 1950s, __Mining__, __Utility and Construction__ are stronger in ratio than that of other decades. In 1960s, health care industry seems to be outnumbered. This is because specialized jobs are required by America Society.

```{r, fig.width=10, fig.height=7}
color <- scales::alpha(c(brewer.pal(n = 9, name = "Pastel1"), brewer.pal(n = 6, name = "Pastel2")), 0.5)
color[2:3] <- c("plum1", "purple")
ggplot(filter(pus.kor, is.na(INDP) == F), aes(x = DECADE)) + 
  geom_bar(aes(fill = INDP), position="fill") +
  scale_fill_manual(values = color) +
  ylab("RATIO") + ggtitle("Industry Distribution by Decade")
```

 The First graph shows that advanced degree(higher than master) people has quite substantial portion of the population. At the second graph, We can guess that there were lots of specialized jobs’ employees especially in __health care__.

```{r, fig.width=9, fig.height=6}
color <- scales::alpha(brewer.pal(n = 7, name = "Pastel1"), 0.5)
color[6:7] <- c("orange", "firebrick1")
ggplot(filter(pus.kor, is.na(SCHL) == F & AGEP >= 35), aes(x=DECADE)) + 
  geom_bar(aes(fill=SCHL), position="fill") + 
  scale_fill_manual(values = color) +
  ylab("RATIO") + ggtitle("Educational Degree")
```

```{r,fig.width=10, fig.height=7}
color <- scales::alpha(c(brewer.pal(n = 9, name = "Pastel1"), brewer.pal(n = 6, name = "Pastel2")), 0.5)
color[10] <- "deeppink"
ggplot(filter(pus.kor, is.na(INDP) == F), aes(x = DECADE)) + 
  geom_bar(aes(fill = INDP), position="fill") +
  scale_fill_manual(values = color) +
  ylab("RATIO") + ggtitle("Industry Distribution by Decade")
```


###1980~90's
 
 In 1980~90's, the number of people engaged in __trade, logistic__ and __other service__ outnumbered the number of people in other decades.
 
```{r, fig.width=10, fig.height=7}
color <- scales::alpha(c(brewer.pal(n = 9, name = "Pastel1"), brewer.pal(n = 6, name = "Pastel2")), 0.5)
color[c(5,11)] <- c("yellowgreen", "seagreen")
ggplot(filter(pus.kor, is.na(INDP) == F), aes(x = DECADE)) + 
  geom_bar(aes(fill = INDP), position="fill") +
  scale_fill_manual(values = color) +
  ylab("RATIO") + ggtitle("Industry Distribution by Decade")
```

###2000's
 In 2000s, __education__ occupation highly increased.
```{r, fig.width=10, fig.height=7}
color <- scales::alpha(c(brewer.pal(n = 9, name = "Pastel1"), brewer.pal(n = 6, name = "Pastel2")), 0.5)
color[9] <- "dodgerblue"
ggplot(filter(pus.kor, is.na(INDP) == F), aes(x = DECADE)) + 
  geom_bar(aes(fill = INDP), position="fill") +
  scale_fill_manual(values = color) +
  ylab("RATIO") + ggtitle("Industry Distribution by Decade")
```

 In 2000’s, percentage of higher than __master degree__ is higher than any other decades, especially __bachelor degree__ is the most highest. And also lower than __highs school or lower degree__ percentage is the lowest.  It seems that during in past 10 years, total educational levels are upward. (Hypothesis : Studying Person’s will be lower than 35 years old)

```{r, fig.width=10, fig.height=7}
color <- scales::alpha(brewer.pal(n = 7, name = "Pastel1"), 0.5)
color[c(1, 6:7)] <-  c("dodgerblue", "orange", "firebrick1")
ggplot(filter(pus.kor, is.na(SCHL) == F & AGEP >= 35), aes(x=DECADE)) + 
  geom_bar(aes(fill=SCHL), position="fill") + 
  scale_fill_manual(values = color) +
  ylab("RATIO") + ggtitle("Educational Degree")
```

### Average Income in Accordance with The Immigration Period by Industries

 The 1950's People have the highest income in __Mining__. Overall, there are high income in __Public Administration__, __Health__ and __Manufacturing__. Especially, there is the best high in 1960's. It sounds obvious, but they have long carrer.

```{r, fig.width=10, fig.height=7}
income.df <- pus.kor %>% filter(is.na(INDP) == F) %>% group_by(DECADE, INDP) %>% summarise(INCOME = mean(PINCP))

income.df$INDP <- factor(income.df$INDP, levels = levels(income.df$INDP)[length(levels(income.df$INDP)):1])
ggplot(income.df, aes(x=DECADE)) + geom_point(aes(y=INDP, size=INCOME, colour=INDP)) +
  ggtitle("Avg. Income by Industry and Immigrant Period") +
  guides(colour=FALSE) + theme_minimal()

income.df$INDP <- factor(income.df$INDP, levels = levels(income.df$INDP)[length(levels(income.df$INDP)):1])
spread(income.df, DECADE, INCOME)
```

